\documentclass[10pt]{article}

% ---------- Page setup ----------
\usepackage[letterpaper,margin=.5in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{fontawesome}
\usepackage{datenumber}
\usepackage{calc}

\pagenumbering{gobble}
\setlength{\parindent}{0pt}

% ---------- Section formatting ----------
\titleformat{\section}
  {\scshape\small}
  {}
  {0pt}
  {\MakeUppercase}
  [\titlerule]

\titlespacing{\section}{0pt}{12pt}{6pt}

\setlist[itemize]{leftmargin=3em, noitemsep, topsep=2pt}

% ---------- Last Experience Duration ----------
\newcounter{datetoday}
\newcounter{diffyears}
\newcounter{diffmonths}
\newcounter{diffdays}


\newcommand{\difftoday}[3]{%
      \setmydatenumber{datetoday}{\the\year}{\the\month}{\the\day}%
      \setmydatenumber{diffdays}{#1}{#2}{#3}%
      \addtocounter{diffdays}{-\thedatetoday}%
      \ifnum\value{diffdays}>0
        \def\diffbefore{in }%
        \def\diffafter{}%
      \else
        \def\diffbefore{}%
        \def\diffafter{ago}%
        \setcounter{diffdays}{-\value{diffdays}}%
      \fi
      \setcounter{diffyears}{\value{diffdays}/365}%
      \setcounter{diffdays}{\value{diffdays}-365*\value{diffyears}}%
      \setcounter{diffmonths}{\value{diffdays}/30}%
      \setcounter{diffdays}{\value{diffdays}-30*\value{diffmonths}}%
      %
      \diffbefore
      \ifnum\value{diffyears}=0
      \else
        \ifnum\value{diffyears}>1
            \thediffyears\space years,
        \else
            \thediffyears\space year,
        \fi
      \fi
      \ifnum\value{diffmonths}=0
      \else
        \ifnum\value{diffmonths}>1
            \thediffmonths\space months
        \else
            \thediffmonths\space month
        \fi
      \fi
      \diffafter
}

% ---------- Custom commands ----------
\newcommand{\resumeItem}[1]{{\small\item #1}}

\newcommand{\resumeSubheading}[4]{
  \textbf{#1} \hfill #2 \\
  \textit{#3} \hfill \textit{#4}
}

\newcommand{\resumeTechs}[1]{
   {\small\textbf{Technologies}: #1}
}

% ---------- Document ----------
\begin{document}

% ---------- Header ----------
\begin{center}
  {\huge \textbf{Omar JIBAR}} \\[4pt]
  {\small DevSecOps Engineer} \\[6pt]
  \faPhone\ 0 669 504 990
  \;|\;\href{mailto:jibaromar@gmail.com}{jibaromar@gmail.com}
  \;|\;\href{https://www.linkedin.com/in/jibaromar}{\faLinkedin\ @jibaromar}
  \;|\;\href{https://github.com/jibaromar}{\faGithub\ @jibaromar}
  \;|\;\href{https://www.youtube.com/@OmarJIBAR/videos}{\faYoutube\ @omarjibar}
  % \;|\;\href{https://www.jibaromar.com}{\faGlobe\ jibaromar.com}
\end{center}

% ---------- Profile ----------
\section*{Profile}
Experienced in network administration, software engineering, and cloud security, I am a DevSecOps Engineer with proven track record of helping organizations 
achieve operational excellence through automation, IaC and CI/CD pipelines. Experienced in Kubernetes-based platforms for both Azure and AWS cloud environments, 
and DevSecOps best practices, including security scanning, monitoring and disaster recovery. Experienced in collaborating closely with development teams, 
and driving reliability, cost optimization and secure software delivery at scale.

% ---------- Skills ----------
\section*{Relevent Skills}
Cloud Migration -- RCA -- Problem Solving -- Disaster Recovery Implementation -- Cost optimization -- Developer Enablement \\
Cross-Team Collaboration -- Technical Documentation 

% ---------- Employment History ----------
\section*{Employment History}

\resumeSubheading
  {DevSecOps Engineer @Thinkproject}
  {June 2024 -- Present}
  {Paris}
  {[\difftoday{2024}{06}{01}]}

\begin{itemize}
  \resumeItem{Designed and maintained Kubernetes CI/CD pipelines, supporting multiple products.}
  \resumeItem{Built and standardized Infrastructure as Code.}
  \resumeItem{Led on-premises to cloud migrations, implementing landing zones and infrastructure architectures.}
  \resumeItem{Enforced repository policies and best practices.}
  \resumeItem{Integrated database change management tool into pipelines.}
  \resumeItem{Implemented monitoring for production environments.}
  \resumeItem{Planned and executed Disaster Recovery and backup tests.}
  \resumeItem{Remediated security vulnerabilities identified by penetration tests and Qualys scans.}
  \resumeItem{Optimized cloud costs and CI/CD performance.}
  \resumeItem{Worked with developers debugging cross-system interoperability issues.}
  \resumeItem{Produced RCA reports to prevent recurrence.}

\end{itemize}

\resumeTechs
  {Kubernetes (AKS), Istio, Helm, Azure Cloud, Azure DevOps, Github Actions, Terraform/Terragrunt, Ansible, Liquibase, Cloudflare, NewRelic, Qualys, Windows Server}

\vspace{12pt}

\resumeSubheading
  {DevSecOps Engineer, @Likewatt}
  {September 2022 -- January 2024}
  {Lyon}
  {[1 year and 4 months]}

\begin{itemize}
  \resumeItem{Set up monitoring and alerts for services.}
  \resumeItem{Designed and implemented a Disaster Recovery strategy for critical services.}
  \resumeItem{Designed, implemented, and maintained CI/CD pipelines.}
  \resumeItem{Designed, developed, and deployed a server-side PDF generation API.}
  \resumeItem{Maintained operational condition and secured production servers.}
  \resumeItem{Migrated a shared file system to a dedicated server.}
  \resumeItem{Documented infrastructure and procedures.}

\end{itemize}

\resumeTechs
  {Terraform, Ansible, Packer, Prometheus, Grafana, Alertmanager, Jenkins, Docker, Kubernetes, Proxmox, Caprover, Firebase, MariaDB, Gitlab, NFS, NodeJS, Express, Handlebars, Flask, Python, Ubuntu, pfSense, OVH}

% ---------- Education ----------
\section*{Education}
{\small
\resumeSubheading
  {Software Cybersecurity Engineering, ENSIBS}
  {2021 -- 2023}
  {Vannes, FR}
  {2 years}

\vspace{3pt}
\resumeSubheading
  {Software Engineering and Distributed Systems Engineering, ENSET}
  {2019 -- 2021}
  {Mohammedia, MAR}
  {2 years}

\vspace{3pt}
\resumeSubheading
  {Network Administration Technician, EST}
  {2016 -- 2018}
  {Sale, MAR}
  {2 years}
}
% ---------- Certificates ----------
\section*{Certificates}

2024 -- \href{https://www.credly.com/badges/253516d8-b087-4f0b-9fb2-19a37b8554b6/public_url}{AWS Certified Solutions Architect -- Associate (expires May 2027)} \\
2024 -- \href{https://www.credly.com/badges/7d4f67e7-e978-469b-bdd6-01cea526ff21/public_url}{Certified Kubernetes Administrator (CKA) (expires Mars 2027)}

\end{document}
